%\section*{Publications}

\renewcommand{\section}[2]{\vspace{2\baselineskip}\refstepcounter{section}{\bf \textsf{#2}}\vspace{0.25\baselineskip}}
\renewcommand{\refname}{Refereed Publications}
\begin{thebibliography}{8}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Mao} {et~al.}(2019){Mao}, {Koda}, {Shapiro}, {Iliev}, {Mellema},
  {Park}, {Ahn}, \& {Bianco}}]{2019arXiv190602476M}
{Mao}, Y., {Koda}, J., {Shapiro}, P.~R., {Iliev}, I.~T., {Mellema}, G., {Park},
  H., {Ahn}, K., \& {Bianco}, M. 2019, ``{The impact of inhomogeneous subgrid
  clumping on cosmic reionization},'' {\em arXiv e-prints\/}, arXiv:1906.02476 (submitted)

\bibitem[{{Carter} {et~al.}(2018){Carter}, {Beutler}, {Percival}, {Blake},
  {Koda}, \& {Ross}}]{2018MNRAS.481.2371C}
{Carter}, P., {Beutler}, F., {Percival}, W.~J., {Blake}, C., {Koda}, J., \&
  {Ross}, A.~J. 2018, ``{Low redshift baryon acoustic oscillation measurement
  from the reconstructed 6-degree field galaxy survey},'' {\em \mnras\/}, {\bf
  481}, 2371

\bibitem[{{Blake} {et~al.}(2018){Blake}, {Carter}, \&
  {Koda}}]{2018MNRAS.479.5168B}
{Blake}, C., {Carter}, P., \& {Koda}, J. 2018, ``{Power spectrum multipoles on
  the curved sky: an application to the 6-degree Field Galaxy Survey},'' {\em
  \mnras\/}, {\bf 479}, 5168

\bibitem[{{Munari} {et~al.}(2017){Munari}, {Monaco}, {Koda}, {Kitaura},
  {Sefusatti}, \& {Borgani}}]{2017JCAP...07..050M}
{Munari}, E., {Monaco}, P., {Koda}, J., {Kitaura}, F.-S., {Sefusatti}, E., \&
  {Borgani}, S. 2017, ``{Testing approximate predictions of displacements of
  cosmological dark matter halos},'' {\em \jcap\/}, {\bf 7}, 050

\bibitem[{{Achitouv} {et~al.}(2017){Achitouv}, {Blake}, {Carter}, {Koda}, \&
  {Beutler}}]{2017PhRvD..95h3502A}
{Achitouv}, I., {Blake}, C., {Carter}, P., {Koda}, J., \& {Beutler}, F. 2017,
  ``{Consistency of the growth rate in different environments with the 6-degree
  Field Galaxy Survey: Measurement of the void-galaxy and galaxy-galaxy
  correlation functions},'' {\em \prd\/}, {\bf 95}, 083502

\bibitem[{{Koda} {et~al.}(2016){Koda}, {Blake}, {Beutler}, {Kazin}, \&
  {Marin}}]{2016MNRAS.459.2118K}
{Koda}, J., {Blake}, C., {Beutler}, F., {Kazin}, E., \& {Marin}, F. 2016,
  ``{Fast and accurate mock catalogue generation for low-mass galaxies},'' {\em
  \mnras\/}, {\bf 459}, 2118

\bibitem[{{Johnson} {et~al.}(2016){Johnson}, {Blake}, {Dossett}, {Koda},
  {Parkinson}, \& {Joudaki}}]{2016MNRAS.458.2725J}
{Johnson}, A., {Blake}, C., {Dossett}, J., {Koda}, J., {Parkinson}, D., \&
  {Joudaki}, S. 2016, ``{Searching for modified gravity: scale and redshift
  dependent constraints from galaxy peculiar velocities},'' {\em \mnras\/},
  {\bf 458}, 2725

\bibitem[{{Scrimgeour} {et~al.}(2016){Scrimgeour}, {Davis}, {Blake},
  {Staveley-Smith}, {Magoulas}, {Springob}, {Beutler}, {Colless}, {Johnson},
  {Jones}, {Koda}, {Lucey}, {Ma}, {Mould}, \& {Poole}}]{2016MNRAS.455..386S}
{Scrimgeour}, M.~I., {Davis}, T.~M., {Blake}, C., {Staveley-Smith}, L.,
  {Magoulas}, C., {Springob}, C.~M., {Beutler}, F., {Colless}, M., {Johnson},
  A., {Jones}, D.~H., {Koda}, J., {Lucey}, J.~R., {Ma}, Y.-Z., {Mould}, J., \&
  {Poole}, G.~B. 2016, ``{The 6dF Galaxy Survey: bulk flows on 50-70 h$^{-1}$
  Mpc scales},'' {\em \mnras\/}, {\bf 455}, 386

\bibitem[{{Mar{\'{\i}}n} {et~al.}(2016){Mar{\'{\i}}n}, {Beutler}, {Blake},
  {Koda}, {Kazin}, \& {Schneider}}]{2016MNRAS.455.4046M}
{Mar{\'{\i}}n}, F.~A., {Beutler}, F., {Blake}, C., {Koda}, J., {Kazin}, E., \&
  {Schneider}, D.~P. 2016, ``{The BOSS-WiggleZ overlap region - II. Dependence
  of cosmic growth on galaxy type},'' {\em \mnras\/}, {\bf 455}, 4046

\bibitem[{{Beutler} {et~al.}(2016){Beutler}, {Blake}, {Koda}, {Mar{\'{\i}}n},
  {Seo}, {Cuesta}, \& {Schneider}}]{2016MNRAS.455.3230B}
{Beutler}, F., {Blake}, C., {Koda}, J., {Mar{\'{\i}}n}, F.~A., {Seo}, H.-J.,
  {Cuesta}, A.~J., \& {Schneider}, D.~P. 2016, ``{The BOSS-WiggleZ overlap
  region - I. Baryon acoustic oscillations},'' {\em \mnras\/}, {\bf 455}, 3230

\bibitem[{{Park} {et~al.}(2016){Park}, {Komatsu}, {Shapiro}, {Koda}, \&
  {Mao}}]{2016ApJ...818...37P}
{Park}, H., {Komatsu}, E., {Shapiro}, P.~R., {Koda}, J., \& {Mao}, Y. 2016,
  ``{The Impact of Nonlinear Structure Formation on the Power Spectrum of
  Transverse Momentum Fluctuations and the Kinetic Sunyaev-Zel'dovich
  Effect},'' {\em \apj\/}, {\bf 818}, 37

\bibitem[{{Koda} {et~al.}(2014){Koda}, {Blake}, {Davis}, {Magoulas},
  {Springob}, {Scrimgeour}, {Johnson}, {Poole}, \&
  {Staveley-Smith}}]{2014MNRAS.445.4267K}
{Koda}, J., {Blake}, C., {Davis}, T., {Magoulas}, C., {Springob}, C.~M.,
  {Scrimgeour}, M., {Johnson}, A., {Poole}, G.~B., \& {Staveley-Smith}, L.
  2014, ``{Are peculiar velocity surveys competitive as a cosmological
  probe?},'' {\em \mnras\/}, {\bf 445}, 4267

\bibitem[{{Johnson} {et~al.}(2014){Johnson}, {Blake}, {Koda}, {Ma}, {Colless},
  {Crocce}, {Davis}, {Jones}, {Magoulas}, {Lucey}, {Mould}, {Scrimgeour}, \&
  {Springob}}]{2014MNRAS.444.3926J}
{Johnson}, A., {Blake}, C., {Koda}, J., {Ma}, Y.-Z., {Colless}, M., {Crocce},
  M., {Davis}, T.~M., {Jones}, H., {Magoulas}, C., {Lucey}, J.~R., {Mould}, J.,
  {Scrimgeour}, M.~I., \& {Springob}, C.~M. 2014, ``{The 6dF Galaxy Survey:
  cosmological constraints from the velocity power spectrum},'' {\em \mnras\/},
  {\bf 444}, 3926

\bibitem[{{Kazin} {et~al.}(2014){Kazin}, {Koda}, {Blake}, {Padmanabhan},
  {Brough}, {Colless}, {Contreras}, {Couch}, {Croom}, {Croton}, {Davis},
  {Drinkwater}, {Forster}, {Gilbank}, {Gladders}, {Glazebrook}, {Jelliffe},
  {Jurek}, {Li}, {Madore}, {Martin}, {Pimbblet}, {Poole}, {Pracy}, {Sharp},
  {Wisnioski}, {Woods}, {Wyder}, \& {Yee}}]{2014MNRAS.441.3524K}
{Kazin}, E.~A., {et~al.} 2014, ``{The WiggleZ Dark Energy Survey: improved
  distance measurements to z = 1 with reconstruction of the baryonic acoustic
  feature},'' {\em \mnras\/}, {\bf 441}, 3524

\bibitem[{{Shapiro} {et~al.}(2013){Shapiro}, {Mao}, {Iliev}, {Mellema},
  {Datta}, {Ahn}, \& {Koda}}]{2013PhRvL.110o1301S}
{Shapiro}, P.~R., {Mao}, Y., {Iliev}, I.~T., {Mellema}, G., {Datta}, K.~K.,
  {Ahn}, K., \& {Koda}, J. 2013, `{\it Will Nonlinear Peculiar Velocity and
  Inhomogeneous Reionization Spoil 21 cm Cosmology from the Epoch of
  Reionization?}', {\em Physical Review Letters\/}, {\bf 110}, 151301

\bibitem[{{Ahn} {et~al.}(2012){Ahn}, {Iliev}, {Shapiro}, {Mellema}, {Koda}, \&
  {Mao}}]{2012ApJ...756L..16A}
{Ahn}, K., {Iliev}, I.~T., {Shapiro}, P.~R., {Mellema}, G., {Koda}, J., \&
  {Mao}, Y. 2012, `{\it Detecting the Rise and Fall of the First Stars by Their
  Impact on Cosmic Reionization}', {\em \apjl\/}, {\bf 756}, L16

\bibitem[{{Iliev} {et~al.}(2012){Iliev}, {Mellema}, {Shapiro}, {Pen}, {Mao},
  {Koda}, \& {Ahn}}]{2012MNRAS.423.2222I}
{Iliev}, I.~T., {Mellema}, G., {Shapiro}, P.~R., {Pen}, U.-L., {Mao}, Y.,
  {Koda}, J., \& {Ahn}, K. 2012, `{\it Can 21-cm observations discriminate between
  high-mass and low-mass galaxies as reionization sources?}', {\em \mnras\/},
  {\bf 423}, 2222

\bibitem[{{Mao} {et~al.}(2012){Mao}, {Shapiro}, {Mellema}, {Iliev}, {Koda}, \&
  {Ahn}}]{2012MNRAS.422..926M}
{Mao}, Y., {Shapiro}, P.~R., {Mellema}, G., {Iliev}, I.~T., {Koda}, J., \&
  {Ahn}, K. 2012, `{\it Redshift-space distortion of the 21-cm background from the
  epoch of reionization - I. Methodology re-examined}', {\em \mnras\/}, {\bf
  422}, 926

%% \bibitem[{{Mao} {et~al.}(2011){Mao}, {Shapiro}, {Mellema}, {Iliev}, {Koda}, \&
%%   {Ahn}}]{2011arXiv1104.2094M}
%% {Mao}, Y., {Shapiro}, P.~R., {Mellema}, G., {Iliev}, I.~T., {Koda}, J., \&
%%   {Ahn}, K. 2011, `{\it Redshift Space Distortion of the 21cm Background from the
%%   Epoch of Reionization I: Methodology Re-examined}', {\em ArXiv e-prints\/},
%%   {MNRAS in press}

%% \bibitem[{{Iliev} {et~al.}(2011){Iliev}, {Mellema}, {Shapiro}, {Pen}, {Mao},
%%   {Koda}, \& {Ahn}}]{2011arXiv1107.4772I}
%% {Iliev}, I.~T., {Mellema}, G., {Shapiro}, P.~R., {Pen}, U.-L., {Mao}, Y.,
%%   {Koda}, J., \& {Ahn}, K. 2011, `{\it Can 21-cm observations discriminate between
%%   high-mass and low-mass galaxies as reionization sources?}', {\em ArXiv
%%   e-prints\/}, {MNRAS submitted}


%% \bibitem[{{Koda} {et~al.}(2010){Koda}, {Ahn}, \& {Shapiro}}]{sidm2}
%% {Koda}, J., {Ahn}, K., \& {Shapiro}, P.~R. 2010, `{\it Evolution of Cosmological
%%   Self-Interacting Dark Matter Haloes: $N$-body simulation versus the fluid
%%   model}', in preparation

\bibitem[{{Koda} \& {Shapiro}(2011)}]{2011MNRAS.415.1125K}
{Koda}, J., \& {Shapiro}, P.~R. 2011, `{\it Gravothermal collapse of isolated
  self-interacting dark matter haloes: N-body simulation versus the fluid
  model}', {\em \mnras\/}, {\bf 415}, 1125

\bibitem[{{Koda} {et~al.}(2009{\natexlab{a}}){Koda}, {Milosavljevic}, \&
  {Shapiro}}]{2009ApJ...696..254K}
{Koda}, J., {Milosavljevic}, M., \& {Shapiro}, P.~R. 2009{\natexlab{a}},
  `{\it On the Survival and Abundance of Disk-dominated Galaxies}', {\em \apj\/},
  {\bf 696}, 254 %, \\(\url{http://ads.nao.ac.jp/abs/2009ApJ...696..254K})

\bibitem[{{Milosavljevic} {et~al.}(2007){Milosavljevic}, {Koda},
  {Nagai}, {Nakar}, \& {Shapiro}}]{2007ApJ...661L.131M}
{Milosavljevic}, M., {Koda}, J., {Nagai}, D., {Nakar}, E., \& {Shapiro},
  P.~R. 2007, `{\it The Cluster-Merger Shock in 1E 0657-56: Faster than a Speeding
  Bullet?}', {\em \apjl\/}, {\bf 661}, L131 %,  \\(\url{http://ads.nao.ac.jp/abs/2007ApJ...661L.131M})

\end{thebibliography}

%\renewcommand{\@biblabel}[1]{#1.}
%% \renewcommand{\refname}{Publications in Preparation}
%% \begin{thebibliography}{8}
%% \setcounter{enumiv}{2}

%% \bibitem[10]{wizcola}
%% {Koda}, J., {Blake} C., {Kazin}, E.~A., {Marin} F.~A., {Beutler} F., 2013, `{\it Multiple realizations of mock galaxy catalogues using the 10-time-step cosmological simulations}',  in preparation
%\end{thebibliography}

%% \bibitem[{{Koda} \& {Shapiro}(2013}})}]{sidm3}
%% {Koda}, J., \& {Shapiro}, P.~R. 2010{\natexlab{b}}, `{\it Statistical Distribution of Self-Interacting Dark
%%   Matter Halo Profiles}', in preparation %, \\(\url{http://www.as.utexas.edu/~junkoda/sidm3.pdf})


\renewcommand{\refname}{PhD Thesis}
\begin{thebibliography}{8}
\bibitem[11]{junkoda.phdthesis}
{Koda}, J. 2009, `{\it Gravitational Dynamics of Halo Formation in a Collisional
  Versus Collisionless Cold Dark Matter Universe}', PhD thesis, The University
  of Texas at Austin
\end{thebibliography}

%% \renewcommand{\refname}{Conference Proceedings}
%% \begin{thebibliography}{8}
%% \bibitem[{{Iliev} {et~al.}(2010){Iliev}, {Ahn}, {Koda}, {Shapiro}, \&
%%   {Pen}}]{2010arXiv1005.2502I}
%% {Iliev}, I.~T., {Ahn}, K., {Koda}, J., {Shapiro}, P.~R., \& {Pen}, U. 2010,
%%   `{\it Cosmic Structure Formation at High Redshift}', arXiv:1005.2502

%% \bibitem[{{Koda} {et~al.}(2009{\natexlab{b}}){Koda}, {Milosavljevic}, \&
%%   {Shapiro}}]{2009arXiv0902.1124K}
%% {Koda}, J., {Milosavljevic}, M., \& {Shapiro}, P.~R. 2009{\natexlab{b}},
%%   `{\it The Impact of Mergers on the Survival and Abundance of Disk-Dominated
%%   Galaxies}', in ASP Conference Series, Galaxy Evolution: Emerging Insights
%%   and Future Challenges, eds. S.~Jogee, L.~Hao, G.~Blanc, \& I.~Marinova


%% \bibitem[{{Koda} {et~al.}(2008){Koda}, {Milosavljevic}, {Shapiro}, {Nagai},
%%   \& {Nakar}}]{2008arXiv0803.1803K}
%% {Koda}, J., {Milosavljevic}, M., {Shapiro}, P.~R., {Nagai}, D., \& {Nakar},
%%   E. 2008, `{\it The Cluster-Merger Shock in 1E 0657-56}', in ASP Conference
%%   Series, New Horizons in Astronomy Frank N. Bash Symposium 2007, eds.
%%   A.~Frebel, J.~R. Maund, J.~Shen, \& M.~H. Siegel
%% \end{thebibliography}

